---
title: "Avazu Click Through Rate Prediction"
author: "NPC"
output:
  html_document:
    keep_md: yes
    toc: yes
---

## Cleanup data
```{r cleanup_data, include=F}
source("Click_through.R")
# train_set = read_data('train',limit=1000)
```
### Proof that data comes from two independent sources website and application
Data is much easier to process if we split it in to two smaller group.  

> **Hypothesis:** We assume that ads from website and application have their own behaviour.  
We can create two models based on different datasources independently.  

```{r proof_split, echo=T}
# proof_split_site_app_domain(train_set)
# remove(train_set)
```

### determine RARE level
To reduce complexity of data, We should separate low occurrence and call them "RARE".
We can still observe "RARE" data if it affects CTR model.
This model counts population of each column. If it less than 1%

> **Hypothesis:** We count population of each column. We assume it is rare if the count is less than 1%.

```{r read_app_web_data, include=F}
# train_web_set = read_data('train',data_source="web", limit=1000)
# train_app_set = read_data('train',data_source="app", limit=1000)
```

```{r cal_rare_level, echo=T}
# m_web = train_model_intersect_prob(train_web_set)
# m_app = train_model_intersect_prob(train_app_set)
# remove(train_web_set)
# remove(train_app_set)
```

### replace rare categories with "RARE"
```{r save_app_index, echo=T, eval=FALSE}
# source("Click_through_cleanup.R")
# save_check_source_index(train_app_set)
# 
# data_sources = c("web", "app")
# data_type    = "train"
# replace_list = c("C1","banner_pos","site_category","app_category", 
#                  "device_model","device_type","device_conn_type",
#                  "C14","C15","C16","C17","C18","C19","C20","C21")
# 
# for (data_source in data_sources) {
#     for (col in replace_list) {
#         cat("Clean", data_type, "set:", data_source, "-", col, "\n")
#         clean_rare_category(col, data_type, data_source)
#     }
# }
```

## Plot and define predictors
We define predictors from clicl index that > 0, that means the feature has click > no-click


### Plot relationship between categories and save score
```{r plot_cat, echo=T}
source("Click_through_plot.R")
plot_category_relation(data_source="web")
# plot_category_relation(data_source="app")
```

### Plot relationship between banners and save score
```{r plot_banner, echo=T}
# plot_banner_misc(data_source="web")
# plot_banner_misc(data_source="app")
```

## Create model from predictors


## Convert raw data into model structure


## Train model


## Evaluate model


## Predict Test set


